---
title: "Application_TCGA"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
date: '`r format(Sys.time(), "%d %B, %Y at %H:%M:%S")`'
---

```{r}
rm(list = ls())
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning = TRUE, message = FALSE, fig.align = "center", fig.ext='png', fig.path = "Application_TCGA/", cache = FALSE)
```

# Packages

```{r, warning=FALSE}
library(factoextra)
library(FactoMineR)

library(aricode)

library(kableExtra)
library(tidyverse)

library(reshape2)
library(ggplot2)
library(ggpubr)
library(gridExtra)
library(ComplexHeatmap)
library(RColorBrewer)
library(circlize)
library(dendextend)

library(igraph)
library(qgraph)
library(corrplot)

library(parallel)
library(huge)

library(limma)
```

#  Functions

```{r}
source("Functions.R")
```

# Settings

```{r}
agreg = "ward.D2"
```

# Division of patients in cancer subtypes

```{r}
load("prot_BRCA.RData") 
```

```{r}
prot_BRCA = prot_BRCA[which(apply(prot_BRCA, 1, FUN = function(x) sum(is.na(x))) == 0),]
```

```{r}
dim(prot_BRCA)
```

```{r}
subtypes = read.table("aims_subtypes.txt")
colnames(prot_BRCA) = substr(colnames(prot_BRCA), 1, nchar(subtypes[1,1]))
colnames(prot_BRCA) = gsub("[.]", "-", colnames(prot_BRCA))
rownames(prot_BRCA) = gsub("[.]", "-", rownames(prot_BRCA)) 
```

```{r}
id_del = colnames(prot_BRCA)[duplicated(colnames(prot_BRCA)) | duplicated(colnames(prot_BRCA), fromLast=TRUE)]
prot_BRCA2 = prot_BRCA[, -which(colnames(prot_BRCA)%in%id_del)]
```

```{r}
id_keep = intersect(colnames(prot_BRCA2), subtypes[,1])
```

```{r}
subtypes = subtypes[subtypes[,1]%in%id_keep, ]
subtypes = subtypes[order(subtypes[,1]),]
```

```{r}
colnames(subtypes) = c("ID", "Subtypes")
```

```{r}
prot_BRCA2 = prot_BRCA2[,colnames(prot_BRCA2)%in%id_keep]
prot_BRCA2 = prot_BRCA2[,order(colnames(prot_BRCA2))]
```

```{r}
identical(colnames(prot_BRCA2), subtypes[,1], attrib.as.set = FALSE)
```

```{r}
prot_BRCA_list = by(t(prot_BRCA2), INDICES = list(subtypes[,2]), FUN = function(x) t(x))
```

```{r}
sapply(prot_BRCA_list, ncol)
```

```{r}
names(prot_BRCA_list) = c("Basal-like", "HER2-enriched", "Luminal A", "Luminal B", "Normal")
```

## Protein selection (limma)

```{r}
designMat = model.matrix(~0+Subtypes, subtypes)
colnames(designMat) = gsub("Subtypes", "", colnames(designMat))
```

```{r}
contrast.matrix = makeContrasts(Basal - (Her2 + LumA + LumB + Normal),
                                Her2 - (Basal + LumA + LumB + Normal),
                                Normal - (Her2 + LumA + LumB + Basal),
                                LumA - (Her2 + Basal + LumB + Normal),
                                LumB - (Her2 + LumA + Basal + Normal), levels = designMat)
```

```{r}
fit <- lmFit(prot_BRCA2, design=designMat)
fit2 = contrasts.fit(fit, contrast.matrix)
fit2 <- eBayes(fit2)
```

```{r}
BasalTab = topTable(fit2, number = 10, coef = "Basal - (Her2 + LumA + LumB + Normal)")
Her2Tab = topTable(fit2, number = 10, coef = "Her2 - (Basal + LumA + LumB + Normal)")
NormalTab = topTable(fit2, number = 10, coef = "Normal - (Her2 + LumA + LumB + Basal)")
LumATab = topTable(fit2, number = 10, coef = "LumA - (Her2 + Basal + LumB + Normal)")
LumBTab = topTable(fit2, number = 10, coef = "LumB - (Her2 + LumA + Basal + Normal)")
```

```{r}
nlim = 5
```


```{r}
prot_keep = unique(c(rownames(BasalTab)[1:nlim], 
                     rownames(Her2Tab)[1:nlim], 
                     # rownames(NormalTab)[1:nlim],
                     rownames(LumATab)[1:nlim], 
                     rownames(LumBTab)[1:nlim]))
```

```{r}
prot_keep
```

```{r}
prot_BRCA_list = lapply(prot_BRCA_list, FUN = function(tab) tab[rownames(tab)%in%prot_keep, ])
```

```{r}
prot_BRCA_list = lapply(prot_BRCA_list, t)
```

```{r}
prot_BRCA_list = lapply(prot_BRCA_list, scale, center = TRUE, scale = TRUE)
```

# Subtypes networks

```{r}
hglasso = mclapply(prot_BRCA_list, huge, lambda.min.ratio = 10^-5, nlambda = 500, method = "glasso", verbose = FALSE, mc.cores = 3)
```

```{r}
bic.select = lapply(hglasso, huge.select, criterion = "ebic", ebic.gamma = 0)
```

```{r}
list_adjacency = lapply(bic.select, FUN = function(x) x$refit)
```

```{r}
sapply(list_adjacency, FUN = function(adj) edge_density(graph_from_adjacency_matrix(adj, mode = "undirected", diag = FALSE), loops = FALSE))
```

```{r, fig.width = 15, fig.height = 3}
par(mfrow = c(1,5))
res = lapply(1:length(list_adjacency), FUN = function(i){
  hc = hclust(as.dist(list_adjacency[[i]]), method = "complete")
  corrplot(list_adjacency[[i]][hc$order, hc$order], is.corr = FALSE, method = "color", diag = FALSE, bg = 'gray85', title = names(list_adjacency)[i], mar = c(0,0.5,1.5,1.5))
})
```

```{r}
densGraph = sapply(list_adjacency, FUN = function(adj) edge_density(graph_from_adjacency_matrix(adj, mode = "undirected", diag = FALSE), loops = FALSE))
list_adjacency = list_adjacency[which(densGraph!=0)]
```

# MFA 

## Shortest path and MDS

```{r}
dist_list = lapply(1:length(list_adjacency), FUN = function(i){
  D = distances(graph_from_adjacency_matrix(list_adjacency[[i]], mode = "undirected"), mode = "all")
  D[is.infinite(D)] = nrow(D)*(nrow(D)-1)/2 + 1 # Nombre d'arcs dans le réseau complet + 1 
  D
})
names(dist_list) = names(list_adjacency)
```

```{r, fig.width = 15, fig.height = 3}
par(mfrow = c(1,5))
res = lapply(1:length(dist_list), FUN = function(i){
  hc = hclust(as.dist(dist_list[[i]]), method = "complete")
  corrplot(dist_list[[i]][hc$order, hc$order], is.corr = FALSE, method = "color", diag = FALSE, bg = 'gray85', title = names(dist_list)[i], mar = c(0,0.5,1.5,1.5))
})
```


```{r}
list_mds = lapply(dist_list, cmdscale, k = nrow(dist_list[[1]])-1)
```

## MFA

```{r}
res_mfa = MFA(do.call("cbind", list_mds),
              group = unlist(lapply(list_mds, ncol)),
              name.group = names(list_mds),
              type = rep("s", length(list_mds)), ncp = Inf, graph = FALSE)
```

```{r, fig.show = "hold", fig.align = "default"}
fviz_eig(res_mfa, addlabels = TRUE)
```

## Heatmap Contribution

```{r, fig.height = 4.5, fig.width=11}
corrplot(res_mfa$group$contrib, method = "circle", mar = c(0, 0, 1.5, 0), bg = "black", diag = TRUE, title = "Contributions all axes", is.corr = FALSE)
```

## Factorial Maps

```{r, fig.height = 3.5 , fig.width = 9}
gg_tab = data.frame(res_mfa$group$coord, "Data" = rownames(res_mfa$group$coord))
xlim_max = max(res_mfa$group$coord[,1]) + 0.05
ylim_max = max(res_mfa$group$coord[,2]) + 0.05

gg1 = ggplot(gg_tab, aes(x = Dim.1, y = Dim.2)) + 
  geom_point() + geom_text(aes(label=rownames(gg_tab)),hjust=1, vjust=1) +
  ggtitle("Axes 1/2") + theme_bw() + xlim(c(-xlim_max,xlim_max)) + ylim(c(0,ylim_max))
gg2 = ggplot(gg_tab, aes(x = Dim.2, y = Dim.3)) + 
  geom_point() + geom_text(aes(label=rownames(gg_tab)),hjust=1, vjust=1) +
  ggtitle("Axes 2/3") + theme_bw()  + xlim(c(-xlim_max,xlim_max)) + ylim(c(0,ylim_max))
gg3 = ggplot(gg_tab, aes(x = Dim.3, y = Dim.4)) + 
  geom_point() + geom_text(aes(label=rownames(gg_tab)),hjust=1, vjust=1) +
  ggtitle("Axes 3/4") + theme_bw()  + xlim(c(-xlim_max,xlim_max)) + ylim(c(0,ylim_max))
gg4 = ggplot(gg_tab, aes(x = Dim.4, y = Dim.5)) + 
  geom_point() + geom_text(aes(label=rownames(gg_tab)),hjust=1, vjust=1) + 
  ggtitle("Axes 4/5") +  theme_bw()  + xlim(c(-xlim_max,xlim_max)) + ylim(c(0,ylim_max))
ggarrange(gg1, gg2, gg3, gg4, ncol = 4, common.legend = TRUE, legend="bottom")
```

```{r}
hc_subtypes = hclust(dist(res_mfa$group$coord), method = agreg)
```

```{r}
DTC_AFM = dynamicTreeCut::cutreeDynamic(hc_subtypes, minClusterSize = 1, distM = as.matrix(dist(res_mfa$group$coord)))
k_cut = max(max(DTC_AFM), 2)
groups = cutree(hc_subtypes, k = k_cut)
```

```{r, fig.height = 6, fig.width = 6.1}
# png(file = "TCGA_hc_subtypes.pdf", width = 1.5*6.3, height = 1.5*6.3, units = "cm", res = 300)
fviz_dend(hc_subtypes, k = k_cut, cex = 0.8, k_colors = c("#2E9FDF", "#00AFBB", "#E7B800", "#FC4E07", "#AA4371"),
          color_labels_by_k = TRUE, ggtheme = theme_bw(), horiz = TRUE, main = "Hierarchical clustering of cancer subtypes",
          labels_track_height = 0.8, lwd = 1) + theme(text = element_text(size = 10), axis.title = element_text(size = 10))
# dev.off()
```

## Heatmap RV

```{r}
corrplot(res_mfa$group$RV, method = "circle", mar = c(0, 0, 1.5, 0), bg = "gray85", diag = FALSE, title = "RV coefficients between MDS datasets", addCoef.col = "antiquewhite")
```

## Consensus network by group

```{r}
consensus_by_groups = lapply(unique(groups), FUN = function(x){
  # x = 1
  list_adj = list_adjacency[names(list_adjacency)%in%names(groups)[groups == x]]
  Adj = Reduce("+", list_adj)
  Adj[Adj<=(0.5*length(list_adj))] = 0
  Adj[Adj>=(0.5*length(list_adj))] = 1
  colnames(Adj) = rownames(Adj) = colnames(prot_BRCA_list[[1]])
  Adj
})
```

```{r, fig.height = 6, fig.width = 6.1}
par(mfrow = c(1,2))
qgraph(consensus_by_groups[[1]], 
       shape = "rectangle", vsize = sapply(colnames(consensus_by_groups[[1]]), nchar)*2.2, vsize2 = 3.5,
       title = paste0("Consensus on ", paste(names(groups)[groups == 1], collapse = ", ")), title.cex = 1,
       mar = c(3,3.5,3,3), color = "antiquewhite", diag = FALSE, 
       labels = colnames(consensus_by_groups[[1]]), label.scale = FALSE, 
       label.cex = 0.7, label.prop = 0.8, negDashed = TRUE, edge.color = "black", edge.width = 0.9, layout = "spring",
       layout.par = list(repulse.rad = nrow(consensus_by_groups[[1]])^(2)))

qgraph(consensus_by_groups[[2]], 
       shape = "rectangle", vsize = sapply(colnames(consensus_by_groups[[2]]), nchar)*2.2, vsize2 = 3.5,
       title = paste0("Consensus on ", paste(names(groups)[groups == 2], collapse = ", ")), title.cex = 1,
       mar = c(3,3.5,3,3), color = "antiquewhite", diag = FALSE, 
       labels = colnames(consensus_by_groups[[1]]), label.scale = FALSE, 
       label.cex = 0.7, label.prop = 0.8, negDashed = TRUE, edge.color = "black", edge.width = 0.9, layout = "spring",
       layout.par = list(repulse.rad = nrow(consensus_by_groups[[2]])^(2)))
```

# Figures (MDS+MFA)

```{r}
library(cowplot)
```


```{r, fig.widht = 15, fig.height = 5}
graphTree = fviz_dend(hc_subtypes, k = k_cut, cex = 0.8, k_colors = c("#2E9FDF", "#00AFBB", "#E7B800", "#FC4E07", "#AA4371"),
          color_labels_by_k = TRUE, ggtheme = theme_bw(), horiz = TRUE, main = "Hierarchical clustering of cancer subtypes",
          labels_track_height = 0.8, lwd = 1) + theme(text = element_text(size = 10), axis.title = element_text(size = 10)) +
  theme(plot.margin = unit(c(0.7,0.5,0.5,0.5), "cm"))
graphTree

# par(mfrow = c(1,2))
qgraph(consensus_by_groups[[1]], 
       shape = "rectangle", vsize = sapply(colnames(consensus_by_groups[[1]]), nchar)*2.2, vsize2 = 3.5,
       title = paste0("Consensus on ", paste(names(groups)[groups == 1], collapse = ", ")), title.cex = 1,
       mar = c(3,3,3,3), color = "antiquewhite", diag = FALSE, 
       labels = colnames(consensus_by_groups[[1]]), label.scale = FALSE, 
       label.cex = 0.7, label.prop = 0.8, negDashed = TRUE, edge.color = "black", edge.width = 0.9, layout = "spring",
       layout.par = list(repulse.rad = nrow(consensus_by_groups[[1]])^(2)))
qg1 = recordPlot()

qgraph(consensus_by_groups[[2]], 
       shape = "rectangle", vsize = sapply(colnames(consensus_by_groups[[2]]), nchar)*2.2, vsize2 = 3.5,
       title = paste0("Consensus on ", paste(names(groups)[groups == 2], collapse = ", ")), title.cex = 1,
       mar = c(3,3,3,3), color = "antiquewhite", diag = FALSE, 
       labels = colnames(consensus_by_groups[[1]]), label.scale = FALSE, 
       label.cex = 0.7, label.prop = 0.8, negDashed = TRUE, edge.color = "black", edge.width = 0.9, layout = "spring",
       layout.par = list(repulse.rad = nrow(consensus_by_groups[[2]])^(2)))

qg2 = recordPlot()

# plot_grid(graphTree, qg1, qg2, labels = 'AUTO', label_size = 12, vjust = 0, hjust = 0, ncol = 3, rel_widths = c(1,1,1), scale = c(0.8, 0.8, 0.8), align = "v")
```

```{r}
ggsave(filename = "Figure10.pdf",  
       plot = ggarrange(ggdraw(graphTree, clip = "on", xlim = c(-0.05, 1)),  ggdraw(qg1, clip = "on", xlim = c(-0.07, 1)),  ggdraw(qg2, clip = "on", xlim = c(-0.07, 1)), ncol = 3,
                        labels = c("A)", "B)", ""), widths = c(1.2, 1, 1)), 
       width = 2*15, height = 2*5, units = c("cm"))
```

# Use of kernel combination method

```{r}
library(mixKernel)
```

## Transformation of shortest path matrices into kernels

```{r}
list_kernel_mat = lapply(dist_list, FUN = function(mat) -double_centering(mat^2)/2)
```

```{r}
list_kernel_mat = lapply(list_kernel_mat, FUN = function(mat){
  eigens = eigen(mat, only.values = FALSE, symmetric = TRUE)
  eigens$vectors[,eigens$values>0]%*%diag(eigens$values[eigens$values>0])%*%t(eigens$vectors[,eigens$values>0])
})
```

## Multiple kernel learning

```{r}
list_kernel_mat = lapply(list_kernel_mat, FUN = function(mat){
  kern = list(kernel = mat, kernel.fun = "shortest_path")
  class(kern) = "kernel"
  kern
})
```

```{r}
list_kernels = list_kernel_mat
```

```{r}
list_args = list_kernels
list_args$method = "full-UMKL"
combKern = do.call(combine.kernels, list_args)
```

```{r}
round(combKern$weights, 3)
combKern$weights
```

```{r}
mat_sim = similarities(list_kernels)
rownames(mat_sim) = colnames(mat_sim) = names(list_kernels)
```

```{r}
mat_dist = DistFromSim(mat_sim)
```

```{r}
hc_samples = hclust(as.dist(mat_dist), method = "complete")
```

```{r}
DTC_Kern = dynamicTreeCut::cutreeDynamic(hc_samples, minClusterSize = 1, distM = as.matrix(as.dist(mat_dist)))
k_cut = max(DTC_Kern)
groups = cutree(hc_samples, k = k_cut)
```


```{r, fig.height = 5, fig.width = 5}
corrplot2(mat_sim, method = "circle", mar = c(0, 0, 0, 0), bg = "gray85", diag = FALSE, tl.cex = 1, tl.col = "black", 
         is.corr = FALSE, addrect = k_cut, order = hc_samples, addCoef.col = "antiquewhite", coef_thresh = 0.5)
corrPlot = recordPlot()
```

```{r, fig.height = 5, fig.width = 5.1}
# png(file = "TCGA_hc_subtypes_kernels.pdf", width = 1.5*6.3, height = 1.5*6.3, units = "cm", res = 300)
graphTree = fviz_dend(hc_samples, k = k_cut, cex = 0.8, k_colors = c("#2E9FDF", "#00AFBB", "#E7B800", "#FC4E07", "#AA4371"),
          color_labels_by_k = TRUE, ggtheme = theme_bw(), horiz = TRUE, main = "Hierarchical clustering of cancer subtypes",
          labels_track_height = 0.8, lwd = 1) + theme(text = element_text(size = 10), axis.title = element_text(size = 10)) +
  theme(plot.margin = unit(c(0.7,0.5,0.5,0.5), "cm"))
graphTree
# dev.off()
graphTree
```

```{r}
ggsave(filename = "Supplementary_TCGA_unused.pdf",
       plot =  ggarrange(ggdraw(graphTree, clip = "on", xlim = c(-0.05, 1)),  ggdraw(corrPlot, clip = "on"), ncol = 2, labels = c("A)", "B)")),
       width = 2*15, height = 2*6.5, units = c("cm"))
```

# InfoSession

```{r}
sessionInfo()
```
