---
title: "Simulations_trees"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
date: '`r format(Sys.time(), "%d %B, %Y at %H:%M:%S")`'
---

```{r}
rm(list = ls())
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning = TRUE, message = FALSE, fig.align = "center", fig.ext='png', fig.path = "Simulations_trees/", cache = FALSE)
```

# Packages

```{r, warning=FALSE}
library(factoextra)
library(FactoMineR)

library(aricode)

library(kableExtra)
library(tidyverse)

library(reshape2)
library(ggplot2)
library(ggpubr)
library(gridExtra)
library(ComplexHeatmap)
library(RColorBrewer)
library(circlize)
library(dendextend)

library(corrplot)
```

```{r}
set.seed(1992)
```

# Functions

```{r}
source("Functions.R")
```

# Data simulation

```{r}
nb_feat = 1000
nb_ind = 100
nb_classif = 3
```

## Classification in each table/tree

```{r}
set.seed(2000)
classif1 = sample(1:4, size = nb_ind, replace = TRUE)
set.seed(1000)
classif2 = sample(1:3, size = nb_ind, replace = TRUE)
set.seed(10^6)
classif3 = sample(1:5, size = nb_ind, replace = TRUE)
```

```{r}
list_clusters = list(classif1, classif2, classif3)
```

```{r}
round(sapply(list_clusters, function(x) sapply(list_clusters, NID, c2 = x)), 3)
round(sapply(list_clusters, function(x) sapply(list_clusters, ARI, c2 = x)), 3)
```

## Table simulation

```{r}
n_dat = 3
```

```{r}
list_sim = unlist(lapply(list_clusters, FUN = function(groups){
  mean_vect = (1:max(groups))[groups]
  lapply(1:n_dat, FUN = function(indice){
    dat = do.call(cbind, lapply(1:nb_feat, FUN = function(i){
      set.seed(i*indice*1000)
      c(rnorm(nb_ind, mean = mean_vect, sd = indice))
    }))
  }) 
}), recursive = FALSE)
```

```{r}
names(list_sim) = paste0("Tree_", 1:length(list_sim))
```


## Trees

```{r}
list_hc = lapply(list_sim, FUN = function(dat) hclust(dist(dat), method = "ward.D2"))
```

```{r}
sapply(list_clusters, FUN = function(classif) sapply(list_hc, FUN = function(hc) ARI(cutree(hc, k = max(classif)), classif)))
```


```{r}
list_hc_b = list_hc[c(1,4,7)]
```

```{r, echo=FALSE, out.width="32%", out.height="20%", fig.show='hold', fig.align="default"}
par(mar = c(2,2,2,0))
res = lapply(1:length(list_hc_b), FUN = function(i){
  hc = list_hc_b[[i]]
  hc$labels = NA
  classif = data.frame("Classif" = c("red", "blue", "green", "magenta", "orange")[list_clusters[[i]]])
  dend = as.dendrogram(hc)
  plot(dend, main = paste0("Arbre ", i)) %>% colored_bars(colors = classif, dend = dend)
})
```

## Data Transformation

```{r}
list_coph = lapply(list_hc, cophenetic)
list_mds = lapply(list_coph, cmdscale, k = nb_ind-1)
```


# MFA 

```{r}
res_mfa = MFA(do.call("cbind", list_mds),
              group = unlist(lapply(list_mds, ncol)),
              name.group = names(list_sim),
              type = rep("c", length(list_mds)), ncp = Inf, graph = FALSE)
```

```{r}
fviz_eig(res_mfa)
```

## Heatmap Contribution

```{r, fig.height = 5, fig.width=12}
corrplot(res_mfa$group$contrib[,1:25], method = "circle", mar = c(0, 0, 1.5, 0), bg = "black", diag = TRUE, title = "Contributions, 25 first axes", is.corr = FALSE)
```

### Factorial Maps

```{r, fig.height = 3.5 , fig.width = 9}
gg_tab = data.frame(res_mfa$group$coord, "Data" = rownames(res_mfa$group$coord), "Classification" = rep(1:3, each = n_dat))
gg_tab$Classification = factor(gg_tab$Classification)

xlim_max = max(res_mfa$group$coord[,1]) + 0.05
ylim_max = max(res_mfa$group$coord[,2]) + 0.05

# "#2E9FDF", "#00AFBB", "#E7B800"
cols = c("1" = "#2E9FDF", "2" = "#E7B800", "3" = "#00AFBB")

gg1 = ggplot(gg_tab, aes(x = Dim.1, y = Dim.2, color = Classification)) + 
  geom_point() + geom_text(aes(label=rownames(gg_tab)), size = 5,hjust=1, vjust=1) +
  ggtitle("Axes 1/2") + theme_bw() + xlim(c(-xlim_max,xlim_max)) + ylim(c(-0.05,ylim_max)) +
  xlab(paste0("Dim 1 - ", round(res_mfa$eig[1,2], 2), "%")) + ylab(paste0("Dim 2 - ", round(res_mfa$eig[2,2], 2), "%")) +
  theme(text = element_text(size = 15), axis.title = element_text(size = 15)) + 
  scale_color_manual(values = cols)
gg2 = ggplot(gg_tab, aes(x = Dim.2, y = Dim.3, color = Classification)) + 
  geom_point() + geom_text(aes(label=rownames(gg_tab)), size = 5,hjust=1, vjust=1) +
  ggtitle("Axes 2/3") + theme_bw()  + xlim(c(-xlim_max,xlim_max)) + ylim(c(-0.05,ylim_max)) +
  xlab(paste0("Dim 2 - ", round(res_mfa$eig[2,2], 2), "%")) + ylab(paste0("Dim 3 - ", round(res_mfa$eig[3,2], 2), "%")) +
  theme(text = element_text(size = 15), axis.title = element_text(size = 15))+ 
  scale_color_manual(values = cols)
gg3 = ggplot(gg_tab, aes(x = Dim.3, y = Dim.4, color = Classification)) + 
  geom_point() + geom_text(aes(label=rownames(gg_tab)), size = 5,hjust=1, vjust=1) +
  ggtitle("Axes 3/4") + theme_bw()  + xlim(c(-xlim_max,xlim_max)) + ylim(c(-0.05,ylim_max)) +
  xlab(paste0("Dim 3 - ", round(res_mfa$eig[3,2], 2), "%")) + ylab(paste0("Dim 4 - ", round(res_mfa$eig[4,2], 2), "%")) +
  theme(text = element_text(size = 15), axis.title = element_text(size = 15)) + 
  scale_color_manual(values = cols)
gg4 = ggplot(gg_tab, aes(x = Dim.4, y = Dim.5, color = Classification)) + 
  geom_point() + geom_text(aes(label=rownames(gg_tab)), size = 5,hjust=1, vjust=1) + 
  ggtitle("Axes 4/5") +  theme_bw()  + xlim(c(-xlim_max,xlim_max)) + ylim(c(-0.05,ylim_max)) +
  xlab(paste0("Dim 4 - ", round(res_mfa$eig[4,2], 2), "%")) + ylab(paste0("Dim 5 - ", round(res_mfa$eig[5,2], 2), "%")) +
  theme(text = element_text(size = 15), axis.title = element_text(size = 15))+ 
  scale_color_manual(values = cols)
```

```{r}
# png(file = "sim_group_pos.png", width = 1.5*9, height = 1.5*4.5, units ="cm", res = 300) 
ggall = ggarrange(gg1, gg2, gg3, gg4, ncol = 2, nrow = 2, common.legend = TRUE, legend="bottom")
# dev.off()
```

```{r}
ggall
```


## Individuals coordinates global MFA

```{r, fig.height = 4, fig.width = 12}
g1_ind = fviz_mfa_ind(res_mfa, geom = "point", col.ind = factor(classif1), legend.title = "Classif 1", title = "")
g2_ind = fviz_mfa_ind(res_mfa, geom = "point", axes = c(2,3), col.ind = factor(classif1), legend.title = "Classif 1", title = "")
g3_ind = fviz_mfa_ind(res_mfa, geom = "point", axes = c(3,4), col.ind = factor(classif1), legend.title = "Classif 1", title = "")
gg_classif1 = ggarrange(g1_ind, g2_ind, g3_ind, ncol = 3, common.legend = TRUE, legend = "right") 
gg_classif1 = annotate_figure(gg_classif1, top = text_grob("Individuals factorial axes - Colored according to classification 1",  vjust = 1.2, face = "bold", size = 14)) + 
  border()
```

```{r, fig.height = 4, fig.width = 12}
g1_ind = fviz_mfa_ind(res_mfa, geom = "point", col.ind = factor(classif2), legend.title = "Classif 2", title = "")
g2_ind = fviz_mfa_ind(res_mfa, geom = "point", axes = c(2,3), col.ind = factor(classif2), legend.title = "Classif 2", title = "")
g3_ind = fviz_mfa_ind(res_mfa, geom = "point", axes = c(3,4), col.ind = factor(classif2), legend.title = "Classif 2", title = "")
gg_classif2 = ggarrange(g1_ind, g2_ind, g3_ind, ncol = 3, common.legend = TRUE, legend = "right") 
gg_classif2 = annotate_figure(gg_classif2, top = text_grob("Individuals factorial axes - Colored according to classification 2",  vjust = 1.2, face = "bold", size = 14)) + 
  border()
```

```{r, fig.height = 4, fig.width = 12}
g1_ind = fviz_mfa_ind(res_mfa, geom = "point", col.ind = factor(classif3), legend.title = "Classif 3", title = "")
g2_ind = fviz_mfa_ind(res_mfa, geom = "point", axes = c(2,3), col.ind = factor(classif3), legend.title = "Classif 3", title = "")
g3_ind = fviz_mfa_ind(res_mfa, geom = "point", axes = c(3,4), col.ind = factor(classif3), legend.title = "Classif 3", title = "")
gg_classif3 = ggarrange(g1_ind, g2_ind, g3_ind, ncol = 3, common.legend = TRUE, legend = "right") 
gg_classif3 = annotate_figure(gg_classif3, top = text_grob("Individuals factorial axes - Colored according to classification 3",  vjust = 1.2, face = "bold", size = 14)) + 
  border()
```

## Data Clustering

```{r}
hc_samples = hclust(dist(res_mfa$group$coord), method = "ward.D2")
```

```{r}
DTC_AFM = dynamicTreeCut::cutreeDynamic(hc_samples, minClusterSize = 1, distM = as.matrix(dist(res_mfa$group$coord)))
k_cut = max(DTC_AFM)
groups = cutree(hc_samples, k = k_cut)
```

```{r}
# par(mar = c(2,2.5,2,0))
# hc = hc_samples
# hc$labels = NA
# dend = as.dendrogram(hc)
# bars = data.frame("DTC" = c("blue", "black", "green", "magenta", "cyan", "orange", "violet")[as.numeric(DTC_AFM)])
# plot(dend, main = "Group of tables") %>% colored_bars(colors = bars, dend = dend, sort_by_labels_order = TRUE)
```

```{r, fig.height = 6, fig.width = 6.1}
# png(file = "sim_hc_tables.png", width = 1.5*9.5, height = 1.5*9.5, units = "cm", res = 300)
fviz_dend(hc_samples, k = k_cut, cex = 1.5,  k_colors = c("#2E9FDF", "#00AFBB", "#E7B800", "#FC4E07", "#AA4371")[1:k_cut],
          color_labels_by_k = TRUE, ggtheme = theme_bw(), horiz = TRUE, main = "Hierarchical clustering of simulated trees",
          labels_track_height = 0.5) + theme(text = element_text(size = 17), axis.title = element_text(size = 15))
# dev.off()
```

```{r, fig.height = 5, fig.width = 5}
# postscript(file = "sim_hc_tables.eps", width = 8, height = 8, horizontal = FALSE, onefile = FALSE, paper = "special")
dendGraph = fviz_dend(hc_samples, k = k_cut, cex = 1,  k_colors = c("#2E9FDF", "#00AFBB", "#E7B800", "#FC4E07", "#AA4371")[1:k_cut],
          color_labels_by_k = TRUE, ggtheme = theme_bw(), horiz = TRUE, main = "Hierarchical clustering of simulated trees",
          labels_track_height = 0.5) + theme(text = element_text(size = 12), axis.title = element_text(size = 12)) + 
  theme(plot.margin = unit(c(0.2,0.1,0,0.1), "cm"), aspect.ratio = 1)
dendGraph
# dev.off()
```

## Heatmap RV

```{r, fig.height = 5, fig.width = 5}
corrplot2(res_mfa$group$RV[-ncol(res_mfa$group$RV), -ncol(res_mfa$group$RV)], method = "circle", mar = c(0, 0, 0, 0), bg = "gray85", diag = FALSE, tl.cex = 1, tl.col = "black", 
          # title = "RV coefficients between MDS datasets",
         is.corr = FALSE, addrect = 3, order = hc_samples, addCoef.col = "antiquewhite", coef_thresh = 0.5)
corrPlot = recordPlot()
```

## Consensus tree on all MFA axes

```{r}
hc_cs = hclust(dist(res_mfa$ind$coord), method = "ward.D2")
```

## Consensus tree on MFA subgroups

```{r}
mds_sublists = lapply(1:k_cut, FUN = function(i) list_mds[names(list_mds)%in%names(groups[groups == i])])
```

```{r}
mfa_sublists = lapply(mds_sublists, FUN = function(liste){
  MFA(do.call("cbind", liste),
              group = unlist(lapply(liste, ncol)),
              name.group = names(liste),
              type = rep("c", length(liste)), ncp = Inf, graph = FALSE)
})
```

```{r, fig.width = 12, fig.height = 5}
grid.arrange(fviz_eig(mfa_sublists[[1]], addlabels = TRUE, main = "Group 1"), 
             fviz_eig(mfa_sublists[[2]], addlabels = TRUE, main = "Group 2"), 
             fviz_eig(mfa_sublists[[3]], addlabels = TRUE, main = "Group 3"),
             ncol = 3)
```

### Heatmaps RV

```{r, fig.height = 4, fig.width = 12}
par(mfrow = c(1,3))
corrplot(mfa_sublists[[1]]$group$RV, method = "circle", mar = c(0, 0, 1.5, 0), bg = "gray85", diag = FALSE, title = "Group 1", tl.cex = 0.8, addCoef.col = "antiquewhite")
corrplot(mfa_sublists[[2]]$group$RV, method = "circle", mar = c(0, 0, 1.5, 0), bg = "gray85", diag = FALSE, title = "Group 2", tl.cex = 0.8, addCoef.col = "antiquewhite")
corrplot(mfa_sublists[[3]]$group$RV, method = "circle", mar = c(0, 0, 1.5, 0), bg = "gray85", diag = FALSE, title = "Group 3", tl.cex = 0.8, addCoef.col = "antiquewhite")
```

### Consensus tree

```{r}
hc_cs_sub = lapply(mfa_sublists, FUN = function(MFARes) hclust(dist(MFARes$ind$coord), method = "ward.D2"))
```

## Comparison of the consensus trees

```{r, fig.height = 3.5, fig.width = 3.5}
par(mar = c(2.5,2.6,1,0))
hc = hc_cs
hc$labels = NA
colors = data.frame(do.call("cbind", lapply(1:length(list_clusters), FUN = function(x)  c("brown", "lightblue", "antiquewhite", "darkorchid3", "orange")[list_clusters[[x]]])))
colnames(colors) = paste0("Class.", 1:length(list_clusters))
plot(as.dendrogram(hc), main = "Consensus Tree on global MFA", cex = 1, cex.axis = 1, cex.main = 1) %>% 
  colored_bars(colors = colors, dend = as.dendrogram(hc), y_shift = -1, cex.rowLabels = 0.9)
```


```{r, fig.height = 5, fig.width = 5, out.width = "30%", fig.show="hold", align = "default"}
par(mar = c(3,2,1,0))
res = lapply(1:length(hc_cs_sub), FUN = function(i){
  hc = hc_cs_sub[[i]]
  hc$labels = NA
  plot(as.dendrogram(hc), main = paste0("Consensus Tree - Group ", i))  %>% colored_bars(colors = colors, dend = as.dendrogram(hc))
})
```

```{r, fig.height = 5, fig.width = 5, out.width = "30%", fig.show="hold", align = "default"}
# res = lapply(1:length(hc_cs_sub), FUN = function(i){
#   png(paste0("sim_trees_", i, ".png"), width = 2*4.75, height = 2*4.75, units = "cm", res = 300)
#   par(mar = c(3,2.2,1,0))
#   hc = hc_cs_sub[[i]]
#   hc$labels = NA
#   plot(as.dendrogram(hc), main = paste0("Consensus Tree - Group ", i))  %>% colored_bars(colors = colors, dend = as.dendrogram(hc))
#   dev.off()
#   })
```

### Comparison with ARI and NID

```{r}
round(sapply(list_clusters, FUN = function(classif) max(apply(cutree(hc_cs, k = 2:length(hc_cs$order)), 2, ARI, c2 = classif))), 2)
```

```{r}
round(sapply(hc_cs_sub, FUN = function(hc){
  sapply(list_clusters, FUN = function(classif) max(apply(cutree(hc, k = 2:length(hc$order)), 2, ARI, c2 = classif)))
}), 2)
```

```{r}
sapply(list_clusters, FUN = function(classif) max(apply(cutree(hc_cs, k = 2:length(hc_cs$order)), 2, NID, c2 = classif)))
```

```{r}
sapply(hc_cs_sub, FUN = function(hc){
  sapply(list_clusters, FUN = function(classif) max(apply(cutree(hc, k = 2:length(hc$order)), 2, NID, c2 = classif)))
})
```

# Figures (MDS+MFA)

```{r}
library(ggplot2)
library(cowplot)
```

## Clustering/RV/Maps

```{r}
ggsave(filename = "Figure1.pdf",  
       plot =  ggarrange(ggdraw(dendGraph, clip = "on", xlim = c(-0.05, 1)),
                         ggdraw(ggall, clip = "on"), ncol = 2,  labels = c("A)", "B)")), 
       width = 2*15, height = 2*6.5,
       units = c("cm"))
```

## Supplementary individual coordinates

```{r}
ggsave(filename = "Supplementary1.pdf",
       plot = ggarrange(gg_classif1, gg_classif2, gg_classif3, labels = c("A)", "B)", "C)"),  ncol = 1), 
       width = 2*12, height = 2*12, units = c("cm"))
```


## Trees

```{r}
par(mar = c(2.5,2.6,2,0))

hc = hc_cs
hc$labels = NA
colors = data.frame(do.call("cbind", lapply(1:length(list_clusters), FUN = function(x)  c("brown", "lightblue", "antiquewhite", "darkorchid3", "orange")[list_clusters[[x]]])))
colnames(colors) = paste0("Class.", 1:length(list_clusters))
plot(as.dendrogram(hc), main = "Consensus Tree \n global MFA", cex = 1, cex.axis = 1, cex.main = 1) %>% 
  colored_bars(colors = colors, dend = as.dendrogram(hc), y_shift = -1, cex.rowLabels = 0.9)
p1 = recordPlot()

hc = hc_cs_sub[[1]]
hc$labels = NA
plot(as.dendrogram(hc), main = paste0("Consensus Tree \n Group ", 1), cex = 1, cex.axis = 1, cex.main = 1)  %>% 
  colored_bars(colors = colors, dend = as.dendrogram(hc), y_shift = -1, cex.rowLabels = 0.9)
p2 = recordPlot()

hc = hc_cs_sub[[2]]
hc$labels = NA
plot(as.dendrogram(hc), main = paste0("Consensus Tree  \n Group ", 2), cex = 1, cex.axis = 1, cex.main = 1)  %>% 
  colored_bars(colors = colors, dend = as.dendrogram(hc), y_shift = -1, cex.rowLabels = 0.9)
p3 = recordPlot()

hc = hc_cs_sub[[3]]
hc$labels = NA
plot(as.dendrogram(hc), main = paste0("Consensus Tree  \n Group ", 3), cex = 1, cex.axis = 1, cex.main = 1)  %>% 
  colored_bars(colors = colors, dend = as.dendrogram(hc), y_shift = -1, cex.rowLabels = 0.9)
p4 = recordPlot()
```

```{r, fig.width = 15, fig.height=5}
ggsave(filename = "Figure2.pdf",  
        plot =    ggarrange(ggdraw(p1, clip = "on"), 
          ggdraw(p2, clip = "on"), 
          ggdraw(p3, clip = "on"), 
          ggdraw(p4, clip = "on"), ncol = 4, labels = ''), width = 2*15, height = 2*5, units = c("cm"))
```

# Multiple Kernel integration

```{r}
library(mixKernel)
```

## From Trees To Kernels

the cophenetic distance is euclidean, its  double-centered matrix (squared) is a Gram matrix (kernel).

```{r}
list_kernel_coph_mat = lapply(list_coph, FUN = function(mat) -double_centering(mat^2)/2)
```

```{r}
# sapply(list_kernel_coph, colMeans)
# sapply(list_kernel_coph, rowMeans)
```

```{r}
list_kernel_coph = lapply(list_kernel_coph_mat, FUN = function(mat){
  kern = list(kernel = mat, kernel.fun = "cophenetic")
  class(kern) = "kernel"
  kern
})
```

## Combinaison des kernels

```{r}
combKern = combine.kernels("Tree_1" = list_kernel_coph$Tree_1,
                           "Tree_2" = list_kernel_coph$Tree_2,
                           "Tree_3" = list_kernel_coph$Tree_3,
                           "Tree_4" = list_kernel_coph$Tree_4,
                           "Tree_5" = list_kernel_coph$Tree_5,
                           "Tree_6" = list_kernel_coph$Tree_6,
                           "Tree_7" = list_kernel_coph$Tree_7,
                           "Tree_8" = list_kernel_coph$Tree_8,
                           "Tree_9" = list_kernel_coph$Tree_9, 
                           method = "full-UMKL")
```

```{r}
round(combKern$weights, 3)
```

```{r}
list_kernels = list("Tree_1" = list_kernel_coph$Tree_1,
                    "Tree_2" = list_kernel_coph$Tree_2,
                    "Tree_3" = list_kernel_coph$Tree_3,
                    "Tree_4" = list_kernel_coph$Tree_4,
                    "Tree_5" = list_kernel_coph$Tree_5,
                    "Tree_6" = list_kernel_coph$Tree_6,
                    "Tree_7" = list_kernel_coph$Tree_7,
                    "Tree_8" = list_kernel_coph$Tree_8,
                    "Tree_9" = list_kernel_coph$Tree_9)
mat_sim = similarities(list_kernels)
rownames(mat_sim) = colnames(mat_sim) = names(list_kernels)
```

Creation of a dissimilarity matrix to build a HC.

```{r}
mat_dist = DistFromSim(mat_sim)
```

```{r}
hc_samples = hclust(as.dist(mat_dist), method = "complete")
```

```{r, fig.height = 5, fig.width = 5}
corrplot2(mat_sim, method = "circle", mar = c(0, 0, 0, 0), bg = "gray85", diag = FALSE, tl.cex = 1, tl.col = "black", 
         is.corr = FALSE, addrect = 3, order = hc_samples, addCoef.col = "antiquewhite", coef_thresh = 0.5)
corrPlot = recordPlot()
```

```{r}
hc_samples = hclust(as.dist(DistFromSim(mat_sim)), method = "complete")
```

```{r}
DTC_Kern = dynamicTreeCut::cutreeDynamic(hc_samples, minClusterSize = 1, distM = as.matrix(as.dist(mat_dist)))
k_cut = max(DTC_Kern)
groups = cutree(hc_samples, k = k_cut)
```

```{r, fig.height = 5, fig.width = 5}
# postscript(file = "sim_hc_tables.eps", width = 8, height = 8, horizontal = FALSE, onefile = FALSE, paper = "special")
dendGraph = fviz_dend(hc_samples, k = 3, cex = 1,  k_colors = c("#2E9FDF", "#00AFBB", "#E7B800", "#FC4E07", "#AA4371")[1:3],
          color_labels_by_k = TRUE, ggtheme = theme_bw(), horiz = TRUE, main = "Hierarchical clustering of simulated trees",
          labels_track_height = 0.5) + theme(text = element_text(size = 12), axis.title = element_text(size = 12)) + 
  theme(plot.margin = unit(c(0,0.1,0,0.1), "cm"), aspect.ratio = 1)
dendGraph
# dev.off()
```
## Consensus tree on overall kernel combination

```{r}
dist_mat = DistFromSim(combKern$kernel)
```

```{r}
hc_cs = hclust(as.dist(dist_mat), method = "complete")
```

```{r}
# png("sim_trees_gKernel.png", width = 2*4.75, height = 2*4.75, units = "cm", res = 300)
par(mar = c(2.3,2.6,1.6,0))
hc = hc_cs
hc$labels = NA
colors = data.frame(do.call("cbind", lapply(1:length(list_clusters), FUN = function(x)  c("brown", "lightblue", "antiquewhite", "darkorchid3", "orange")[list_clusters[[x]]])))
colnames(colors) = paste0("Class.", 1:length(list_clusters))
plot(as.dendrogram(hc), main = "Consensus Tree on \n global kernel combination", cex = 1, cex.axis = 1, cex.main = 1) %>% 
  colored_bars(colors = colors, dend = as.dendrogram(hc), y_shift = -0.2, cex.rowLabels = 0.9)
# dev.off()
```

## Consensus trees on each subgroup

```{r}
kernels_sublists = lapply(1:k_cut, FUN = function(i) list_kernels[names(list_kernels)%in%names(groups[groups == i])])
```

```{r}
combKern = combine.kernels("Tree_1" = list_kernel_coph$Tree_1,
                           "Tree_2" = list_kernel_coph$Tree_2,
                           "Tree_3" = list_kernel_coph$Tree_3,
                           "Tree_4" = list_kernel_coph$Tree_4,
                           "Tree_5" = list_kernel_coph$Tree_5,
                           "Tree_6" = list_kernel_coph$Tree_6,
                           "Tree_7" = list_kernel_coph$Tree_7,
                           "Tree_8" = list_kernel_coph$Tree_8,
                           "Tree_9" = list_kernel_coph$Tree_9,
                           method = "full-UMKL")
```

```{r}
round(combKern$weights, 3)
```

```{r}
kernels_comb = lapply(kernels_sublists, FUN = function(sublist){
  arg_list = sublist
  arg_list$method = "full-UMKL"
  do.call(combine.kernels, arg_list)
})
```

```{r}
hc_cs_sub = lapply(kernels_comb, FUN = function(kernels) hclust(as.dist(DistFromSim(kernels$kernel)), method = "complete"))
```

```{r}
par(mar = c(2.5,2.6,2,0))

hc = hc_cs
hc$labels = NA
colors = data.frame(do.call("cbind", lapply(1:length(list_clusters), FUN = function(x)  c("brown", "lightblue", "antiquewhite", "darkorchid3", "orange")[list_clusters[[x]]])))
colnames(colors) = paste0("Class.", 1:length(list_clusters))
plot(as.dendrogram(hc), main = "Consensus Tree \n global kernel combination", cex = 1, cex.axis = 1, cex.main = 1) %>% 
  colored_bars(colors = colors, dend = as.dendrogram(hc), y_shift = -0.1, cex.rowLabels = 0.9)
p1 = recordPlot()

hc = hc_cs_sub[[1]]
hc$labels = NA
plot(as.dendrogram(hc), main = paste0("Consensus Tree \n Group ", 1, " - Kernel"), cex = 1, cex.axis = 1, cex.main = 1)  %>% 
  colored_bars(colors = colors, dend = as.dendrogram(hc), y_shift = -0.1, cex.rowLabels = 0.9)
p2 = recordPlot()

hc = hc_cs_sub[[2]]
hc$labels = NA
plot(as.dendrogram(hc), main = paste0("Consensus Tree  \n Group ", 2, " - Kernel"), cex = 1, cex.axis = 1, cex.main = 1)  %>% 
  colored_bars(colors = colors, dend = as.dendrogram(hc), y_shift = -0.1, cex.rowLabels = 0.9)
p3 = recordPlot()

hc = hc_cs_sub[[3]]
hc$labels = NA
plot(as.dendrogram(hc), main = paste0("Consensus Tree  \n Group ", 3, " - Kernel"), cex = 1, cex.axis = 1, cex.main = 1)  %>% 
  colored_bars(colors = colors, dend = as.dendrogram(hc), y_shift = -0.1, cex.rowLabels = 0.9)
p4 = recordPlot()
```

### Comparison with ARI and NID

```{r}
round(sapply(list_clusters, FUN = function(classif) max(apply(cutree(hc_cs, k = 2:length(hc_cs$order)), 2, ARI, c2 = classif))), 2)
```

```{r}
round(sapply(hc_cs_sub, FUN = function(hc){
  sapply(list_clusters, FUN = function(classif) max(apply(cutree(hc, k = 2:length(hc$order)), 2, ARI, c2 = classif)))
}), 2)
```

```{r}
sapply(list_clusters, FUN = function(classif) max(apply(cutree(hc_cs, k = 2:length(hc_cs$order)), 2, NID, c2 = classif)))
```

```{r}
sapply(hc_cs_sub, FUN = function(hc){
  sapply(list_clusters, FUN = function(classif) max(apply(cutree(hc, k = 2:length(hc$order)), 2, NID, c2 = classif)))
})
```

# Figures (kernels)

```{r}
ggsave(filename = "Figure3.pdf",  
       plot =  ggarrange(ggdraw(dendGraph, clip = "on", xlim = c(-0.05, 1)),  ggdraw(corrPlot, clip = "on"), ncol = 2, labels = c("A)", "B)")),
       width = 2*15, height = 2*6.5, units = c("cm"))
```

```{r, fig.width = 15, fig.height=5}
ggsave(filename = "Figure4.pdf",  
        plot =    ggarrange(ggdraw(p1, clip = "on"), 
          ggdraw(p2, clip = "on"), 
          ggdraw(p3, clip = "on"), 
          ggdraw(p4, clip = "on"), ncol = 4, labels = ''), width = 2*15, height = 2*5, units = c("cm"))
```

# InfoSession

```{r}
sessionInfo()
```
