---
title: "Simulations_network"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
date: '`r format(Sys.time(), "%d %B, %Y at %H:%M:%S")`'
---

```{r}
rm(list = ls())
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning = TRUE, message = FALSE, fig.align = "center", fig.ext='png', fig.path = "Simulations_network/", cache = FALSE)
```

# Packages

```{r, warning=FALSE}
library(factoextra)
library(FactoMineR)

library(aricode)

library(kableExtra)
library(tidyverse)

library(reshape2)
library(ggplot2)
library(ggpubr)
library(gridExtra)
library(ComplexHeatmap)
library(RColorBrewer)
library(circlize)
library(dendextend)

library(qgraph)
library(igraph)
library(corrplot)
```

```{r}
set.seed(1992)
```


#  Fonctions utiles

```{r}
source("Functions.R")
```

# Network simulation

## Settings

```{r}
nb_ind =  100
```

```{r}
set.seed(2000)
classif1 = sample(1:4, size = nb_ind, replace = TRUE)
set.seed(1000)
classif2 = sample(1:3, size = nb_ind, replace = TRUE)
set.seed(10^6)
classif3 = sample(1:5, size = nb_ind, replace = TRUE)
```

```{r}
list_clusters = list(classif1, classif2, classif3)
```

```{r}
round(sapply(list_clusters, function(x) sapply(list_clusters, ARI, c2 = x)), 3)
```

```{r}
n_net = 3 
```

```{r}
prob_inside = 0.80 # probability of an edge between two nodes of the same cluster
prob_outside = 0.05 # probability of an edge between two nodes that are not in the same cluster
```

## Network simulation

```{r}
list_sim = unlist(lapply(list_clusters, FUN = function(groups){
  matEdgesProb = matrix(prob_outside, nrow = max(groups), ncol = max(groups))
  diag(matEdgesProb) = prob_inside
  matEdgesProb = matEdgesProb[groups, groups]
  mean_mat =  matrix(0.1, nrow = max(groups), ncol = max(groups))
  diag(mean_mat) = (1:max(groups))
  mean_mat = mean_mat[groups, groups]
  
  lapply(1:n_net, FUN = function(indice){
  
    A =  matrix(0, ncol = length(groups), nrow = length(groups))
    set.seed(indice*1000)
    A = matrix(rbinom(length(groups)^2, 1, prob = matEdgesProb), ncol = length(groups), nrow = length(groups))    
    A[lower.tri(A, diag = FALSE)] = t(A)[lower.tri(A, diag = FALSE)]
    
    return(list(A = A))
    }) 
}), recursive = FALSE)
```

```{r}
names(list_sim) = paste0("Net_", 1:length(list_sim))
```

## Adjancecy matrices

```{r}
list_adjacency = lapply(list_sim, FUN  = function(res) res$A)
```

```{r, fig.width = 12, fig.height = 4}
par(mfrow = c(1,3))
corrplot(list_adjacency[[1]][order(list_clusters[[1]]), order(list_clusters[[1]])], is.corr = FALSE, method = "color", diag = FALSE, bg = 'gray85')
corrplot(list_adjacency[[4]][order(list_clusters[[2]]), order(list_clusters[[2]])], is.corr = FALSE, method = "color", diag = FALSE, bg = 'gray85')
corrplot(list_adjacency[[7]][order(list_clusters[[3]]), order(list_clusters[[3]])], is.corr = FALSE, method = "color", diag = FALSE, bg = 'gray85')
```

# MFA on adjacency matrices

## Shortest path and MDS

```{r}
dist_list = lapply(1:length(list_adjacency), FUN = function(i) distances(graph_from_adjacency_matrix(list_adjacency[[i]], mode = "undirected"), mode = "all"))
```

```{r, fig.width = 12, fig.height = 4}
par(mfrow = c(1,3))
corrplot(dist_list[[1]][order(list_clusters[[1]]), order(list_clusters[[1]])], is.corr = FALSE, method = "color", diag = FALSE, bg = 'gray85')
corrplot(dist_list[[4]][order(list_clusters[[2]]), order(list_clusters[[2]])], is.corr = FALSE, method = "color", diag = FALSE, bg = 'gray85')
corrplot(dist_list[[7]][order(list_clusters[[3]]), order(list_clusters[[3]])], is.corr = FALSE, method = "color", diag = FALSE, bg = 'gray85')
```

```{r}
list_mds = lapply(dist_list, cmdscale, k = nb_ind-1)
```

## MFA 

```{r}
res_mfa = MFA(do.call("cbind", list_mds),
              group = unlist(lapply(list_mds, ncol)),
              name.group = names(list_sim),
              type = rep("c", length(list_mds)), ncp = Inf, graph = FALSE)
```

```{r}
fviz_eig(res_mfa, choice = "variance", addlabels = TRUE)
```

## Heatmap Contribution

```{r, fig.height = 5, fig.width=12}
corrplot(res_mfa$group$contrib[,1:25], method = "circle", mar = c(0, 0, 1.5, 0), bg = "black", diag = TRUE, title = "Contributions, 25 first axes", is.corr = FALSE)
```

## Factorial Maps

```{r, fig.height = 3.5 , fig.width = 9}
gg_tab = data.frame(res_mfa$group$coord, "Data" = rownames(res_mfa$group$coord), "Classification" = rep(1:3, each = n_net))
gg_tab$Classification = factor(gg_tab$Classification)

xlim_max = max(res_mfa$group$coord) + 0.05
xlim_min = -0.1
ylim_max = max(res_mfa$group$coord) + 0.05

cols = c("1" = "#E7B800", "2" = "#00AFBB", "3" = "#2E9FDF")

gg1 = ggplot(gg_tab, aes(x = Dim.1, y = Dim.2, color = Classification)) + 
  geom_point() + geom_text(aes(label=rownames(gg_tab)), size = 5,hjust=1, vjust=1) + 
  ggtitle("Axes 1/2") + theme_bw() + xlim(c(xlim_min, xlim_max)) + ylim(c(-0.05, ylim_max)) +
  xlab(paste0("Dim 1 - ", round(res_mfa$eig[1,2], 2), "%")) + ylab(paste0("Dim 2 - ", round(res_mfa$eig[2,2], 2), "%")) +
  theme(text = element_text(size = 15), axis.title = element_text(size = 15))+ 
  scale_color_manual(values = cols)
gg2 = ggplot(gg_tab, aes(x = Dim.2, y = Dim.3, color = Classification)) + 
  geom_point() + geom_text(aes(label=rownames(gg_tab)), size = 5,hjust=1, vjust=1) + 
  ggtitle("Axes 2/3") + theme_bw()  + xlim(c(xlim_min,xlim_max)) + ylim(c(-0.05,ylim_max)) +
  xlab(paste0("Dim 2 - ", round(res_mfa$eig[2,2], 2), "%")) + ylab(paste0("Dim 3 - ", round(res_mfa$eig[3,2], 2), "%")) +
  theme(text = element_text(size = 15), axis.title = element_text(size = 15))+ 
  scale_color_manual(values = cols)
gg3 = ggplot(gg_tab, aes(x = Dim.3, y = Dim.4, color = Classification)) + 
  geom_point() + geom_text(aes(label=rownames(gg_tab)), size = 5,hjust=1, vjust=1) + 
  ggtitle("Axes 3/4") + theme_bw()  + xlim(c(xlim_min,xlim_max)) + ylim(c(-0.05,ylim_max)) +
  xlab(paste0("Dim 3 - ", round(res_mfa$eig[3,2], 2), "%")) + ylab(paste0("Dim 4 - ", round(res_mfa$eig[4,2], 2), "%")) +
  theme(text = element_text(size = 15), axis.title = element_text(size = 15))+ 
  scale_color_manual(values = cols)
gg4 = ggplot(gg_tab, aes(x = Dim.4, y = Dim.5, color = Classification)) + 
  geom_point() + geom_text(aes(label=rownames(gg_tab)), size = 5,hjust=1, vjust=1) + 
  ggtitle("Axes 4/5") +  theme_bw()  + xlim(c(xlim_min,xlim_max)) + ylim(c(-0.05,ylim_max)) +
  xlab(paste0("Dim 4 - ", round(res_mfa$eig[4,2], 2), "%")) + ylab(paste0("Dim 5 - ", round(res_mfa$eig[5,2], 2), "%")) +
  theme(text = element_text(size = 15), axis.title = element_text(size = 15))+ 
  scale_color_manual(values = cols)
```

```{r, fig.height = 6, fig.width = 6.1}
# postscript(file = "sim_net_group_pos.eps", width = 12, height = 3, horizontal = FALSE, onefile = FALSE, paper = "special")
# ggarrange(gg1, gg2, gg3, gg4, ncol = 2, nrow = 2, common.legend = TRUE, legend="bottom")  
# dev.off()
```

```{r, fig.height = 6, fig.width = 6.1}
# png(file = "sim_net_group_pos.png", width = 1.5*19, height = 1.5*4.5, units ="cm", res = 300) 
ggall = ggarrange(gg1, gg2, gg3, gg4,  ncol = 2, nrow = 2, common.legend = TRUE, legend="bottom")
# dev.off()
ggall
```

```{r}
hc_samples = hclust(dist(res_mfa$group$coord), method = "ward.D2")
```

```{r}
DTC_AFM = dynamicTreeCut::cutreeDynamic(hc_samples, minClusterSize = 1, distM = as.matrix(dist(res_mfa$group$coord)))
k_cut = max(DTC_AFM)
groups = cutree(hc_samples, k = k_cut)
```

```{r, fig.height = 6, fig.width = 6.1}
# png(file = "sim_net_hc_tables.png", width = 1.5*9.5, height = 1.5*9.5, units = "cm", res = 300)
dendGraph = fviz_dend(hc_samples, k = k_cut, cex = 1.2,  k_colors = c("#2E9FDF", "#00AFBB", "#E7B800", "#FC4E07", "#AA4371")[1:k_cut],
          color_labels_by_k = TRUE, ggtheme = theme_bw(), horiz = TRUE, main = "Hierarchical clustering of simulated networks",
          labels_track_height = 0.3)  + theme(text = element_text(size = 14), axis.title = element_text(size = 11))
dendGraph
# dev.off()
```

## Heatmap RV

```{r}
corrplot2(res_mfa$group$RV, method = "circle", mar = c(0, 0, 0, 0), bg = "gray85", diag = FALSE, tl.cex = 1.5, tl.col = "black", 
          # title = "RV coefficients between MDS datasets",
         is.corr = FALSE, addrect = 3, order = hc_samples, addCoef.col = "antiquewhite", coef_thresh = 0.5)
corrPlot = recordPlot()
```

## Individuals coordinates global MFA

```{r, fig.height = 4, fig.width = 12}
g1_ind = fviz_mfa_ind(res_mfa, geom = "point", col.ind = factor(classif1), legend.title = "Classif 1", title = "")
g2_ind = fviz_mfa_ind(res_mfa, geom = "point", axes = c(2,3), col.ind = factor(classif1), legend.title = "Classif 1", title = "")
g3_ind = fviz_mfa_ind(res_mfa, geom = "point", axes = c(3,4), col.ind = factor(classif1), legend.title = "Classif 1", title = "")
gg_classif1 = ggarrange(g1_ind, g2_ind, g3_ind, ncol = 3, common.legend = TRUE, legend = "right") 
gg_classif1 = annotate_figure(gg_classif1, top = text_grob("Individuals factorial axes - Colored according to classification 1",  vjust = 1.2, face = "bold", size = 14)) + 
  border()
```

```{r, fig.height = 4, fig.width = 12}
g1_ind = fviz_mfa_ind(res_mfa, geom = "point", col.ind = factor(classif2), legend.title = "Classif 2", title = "")
g2_ind = fviz_mfa_ind(res_mfa, geom = "point", axes = c(2,3), col.ind = factor(classif2), legend.title = "Classif 2", title = "")
g3_ind = fviz_mfa_ind(res_mfa, geom = "point", axes = c(3,4), col.ind = factor(classif2), legend.title = "Classif 2", title = "")
gg_classif2 = ggarrange(g1_ind, g2_ind, g3_ind, ncol = 3, common.legend = TRUE, legend = "right") 
gg_classif2 = annotate_figure(gg_classif2, top = text_grob("Individuals factorial axes - Colored according to classification 2",  vjust = 1.2, face = "bold", size = 14)) + 
  border()
```

```{r, fig.height = 4, fig.width = 12}
g1_ind = fviz_mfa_ind(res_mfa, geom = "point", col.ind = factor(classif3), legend.title = "Classif 3", title = "")
g2_ind = fviz_mfa_ind(res_mfa, geom = "point", axes = c(2,3), col.ind = factor(classif3), legend.title = "Classif 3", title = "")
g3_ind = fviz_mfa_ind(res_mfa, geom = "point", axes = c(3,4), col.ind = factor(classif3), legend.title = "Classif 3", title = "")
gg_classif3 = ggarrange(g1_ind, g2_ind, g3_ind, ncol = 3, common.legend = TRUE, legend = "right") 
gg_classif3 = annotate_figure(gg_classif3, top = text_grob("Individuals factorial axes - Colored according to classification 3",  vjust = 1.2, face = "bold", size = 14)) + 
  border()
```

## Consensus network(s)

```{r}
consensus_by_groups = lapply(unique(groups), FUN = function(x){
  list_adj = list_adjacency[names(list_adjacency)%in%names(groups)[groups == x]]
  Adj = Reduce("+", list_adj)
  Adj[Adj<=(0.5*length(list_adj))] = 0
  Adj[Adj>=(0.5*length(list_adj))] = 1
  Adj
})
```

```{r}
consensus_by_groups_MFA = consensus_by_groups
```

```{r}
round(sapply(consensus_by_groups, FUN = function(A_e){
  sapply(list_adjacency, FUN = function(A_t) sum(abs(as.matrix(A_e) - as.matrix(A_t)))/ncol(A_e)^2)
  }),2)
```

```{r}
res = lapply(consensus_by_groups, FUN = function(A_e){
  sapply(list_adjacency, FUN = function(A_t){
    vect = round(compareGraphs_perso(A_e, A_t), 2)
    names(vect) = c("tpr", "fpr", "tdr")
    vect})
})
names(res) = paste("Consensus ", 1:length(consensus_by_groups))
```

```{r}
names_above = c(rep(3, 3))
names(names_above) = c(names(res))
df = do.call("rbind", res)
tab = kable(df, format = "latex") %>% kable_styling() %>% pack_rows(index = names_above)
```


```{r, fig.height = 5, fig.width = 15}
par(mfrow = c(1,3))
qgraph(consensus_by_groups[[1]], 
       shape = "rectangle", vsize = 2, vsize2 = 2.2,
       title = paste0("Consensus on ", paste(names(groups)[groups == 1], collapse = ", ")),
       mar = c(2,2,2,2), color = c("antiquewhite", "aliceblue", "darkorchid3", "forestgreen", "blue")[classif1], diag = FALSE, 
       labels = colnames(consensus_by_groups[[1]]), title.cex = 2,
       label.cex = 1.2, negDashed = TRUE, edge.color = "black", edge.width = 0.5, layout = "spring",
       layout.par = list(repulse.rad = nrow(consensus_by_groups[[1]])^(2.5)))

qgraph(consensus_by_groups[[2]], 
       shape = "rectangle", vsize = 2, vsize2 = 2.2,
       title = paste0("Consensus on ", paste(names(groups)[groups == 2], collapse = ", ")),
       mar = c(2,2,2,2), color =  c("antiquewhite", "aliceblue", "darkorchid3", "forestgreen", "blue")[classif2], diag = FALSE, 
       labels = colnames(consensus_by_groups[[2]]), title.cex = 2,
       label.cex = 1.2, negDashed = TRUE, edge.color = "black", edge.width = 0.5, layout = "spring",
       layout.par = list(repulse.rad = nrow(consensus_by_groups[[2]])^(2.5)))

qgraph(consensus_by_groups[[3]], 
       shape = "rectangle", vsize = 2, vsize2 = 2.2,
       title = paste0("Consensus on ", paste(names(groups)[groups == 3], collapse = ", ")),
       mar = c(2,2,2,2), color =  c("antiquewhite", "aliceblue", "darkorchid3", "forestgreen", "blue")[classif3], diag = FALSE, 
       labels = colnames(consensus_by_groups[[3]]), title.cex = 2,
       label.cex = 1.2, negDashed = TRUE, edge.color = "black", edge.width = 0.5, layout = "spring",
       layout.par = list(repulse.rad = nrow(consensus_by_groups[[3]])^(2.5)))

conGraph = recordPlot()
```

# Figures (MDS+MFA)

```{r}
library(ggplot2)
library(cowplot)
```

## Clustering/ Group Maps

```{r}
ggsave(filename = "Figure5.pdf",  
       plot =  ggarrange(ggdraw(dendGraph, clip = "on", xlim = c(-0.05, 1)),
                         ggdraw(ggall, clip = "on"), ncol = 2,  labels = c("A)", "B)")), 
       width = 2*15, height = 2*6.5,
       units = c("cm"))
```

## Supplementary individual coordinates

```{r}
ggsave(filename = "Supplementary_unused_networks.pdf",
       plot = ggarrange(gg_classif1, gg_classif2, gg_classif3, labels = c("A)", "B)", "C)"),  ncol = 1), 
       width = 2*12, height = 2*12, units = c("cm"))
```

## Consensus networks

```{r, fig.height = 5, fig.width = 15}
png(file = "Figure6.png", width = 2*15, height = 2*5, units = "cm", res = 300)
par(mfrow = c(1,3))
qgraph(consensus_by_groups[[1]], 
       shape = "rectangle", vsize = 2, vsize2 = 2.2,
       title = paste0("Consensus on ", paste(names(groups)[groups == 1], collapse = ", ")),
       mar = c(2,2,2,2), color = c("antiquewhite", "aliceblue", "darkorchid3", "forestgreen", "blue")[classif1], diag = FALSE, 
       labels = colnames(consensus_by_groups[[1]]), title.cex = 1.5,
       label.cex = 1.2, negDashed = TRUE, edge.color = "black", edge.width = 0.9, layout = "spring",
       layout.par = list(repulse.rad = nrow(consensus_by_groups[[1]])^(2.5)))

qgraph(consensus_by_groups[[2]], 
       shape = "rectangle", vsize = 2, vsize2 = 2.2,
       title = paste0("Consensus on ", paste(names(groups)[groups == 2], collapse = ", ")),
       mar = c(2,2,2,2), color =  c("antiquewhite", "aliceblue", "darkorchid3", "forestgreen", "blue")[classif2], diag = FALSE, 
       labels = colnames(consensus_by_groups[[2]]), title.cex = 1.5,
       label.cex = 1.2, negDashed = TRUE, edge.color = "black", edge.width = 0.9, layout = "spring",
       layout.par = list(repulse.rad = nrow(consensus_by_groups[[2]])^(2.5)))

qgraph(consensus_by_groups[[3]], 
       shape = "rectangle", vsize = 2, vsize2 = 2.2,
       title = paste0("Consensus on ", paste(names(groups)[groups == 3], collapse = ", ")),
       mar = c(2,2,2,2), color =  c("antiquewhite", "aliceblue", "darkorchid3", "forestgreen", "blue")[classif3], diag = FALSE, 
       labels = colnames(consensus_by_groups[[3]]), title.cex = 1.5,
       label.cex = 1.2, negDashed = TRUE, edge.color = "black", edge.width = 0.9, layout = "spring",
       layout.par = list(repulse.rad = nrow(consensus_by_groups[[3]])^(2.5)))
dev.off()
```

# Simulations with kernels

```{r}
library(mixKernel)
```

## Transformation of shortest path matrices into kernels

```{r}
names(dist_list) = names(list_sim)
```

```{r}
list_kernel_mat = lapply(dist_list, FUN = function(mat) -double_centering(mat^2)/2)
```

```{r}
list_kernel_mat = lapply(list_kernel_mat, FUN = function(mat){
  eigens = eigen(mat, only.values = FALSE, symmetric = TRUE)
  eigens$vectors[,eigens$values>0]%*%diag(eigens$values[eigens$values>0])%*%t(eigens$vectors[,eigens$values>0])
})
```

## Combinaison des kernels

```{r}
list_kernel_mat = lapply(list_kernel_mat, FUN = function(mat){
  kern = list(kernel = mat, kernel.fun = "shortest_path")
  class(kern) = "kernel"
  kern
})
```

```{r}
list_kernels = list("Net_1" = list_kernel_mat$Net_1,
           "Net_2" = list_kernel_mat$Net_2,
           "Net_3" = list_kernel_mat$Net_3,
           "Net_4" = list_kernel_mat$Net_4,
           "Net_5" = list_kernel_mat$Net_5,
           "Net_6" = list_kernel_mat$Net_6,
           "Net_7" = list_kernel_mat$Net_7,
           "Net_8" = list_kernel_mat$Net_8,
           "Net_9" = list_kernel_mat$Net_9)
```

```{r}
list_args = list_kernels
list_args$method = "full-UMKL"
combKern = do.call(combine.kernels, list_args)
```

```{r}
round(combKern$weights, 3)
combKern$weights
```

```{r}
mat_sim = similarities(list_kernels)
rownames(mat_sim) = colnames(mat_sim) = names(list_kernels)
```

```{r}
mat_dist = DistFromSim(mat_sim)
```

```{r}
hc_samples = hclust(as.dist(mat_dist), method = "complete")
```

```{r, fig.height = 5, fig.width = 5}
corrplot2(mat_sim, method = "circle", mar = c(0, 0, 0, 0), bg = "gray85", diag = FALSE, tl.cex = 1, tl.col = "black", 
         is.corr = FALSE, addrect = 3, order = hc_samples, addCoef.col = "antiquewhite", coef_thresh = 0.5)
corrPlot = recordPlot()
```

```{r}
hc_samples = hclust(as.dist(DistFromSim(mat_sim)), method = "complete")
```

```{r}
DTC_Kern = dynamicTreeCut::cutreeDynamic(hc_samples, minClusterSize = 1, distM = as.matrix(as.dist(mat_dist)))
k_cut = max(DTC_Kern)
groups = cutree(hc_samples, k = k_cut)
```

```{r, fig.height = 6, fig.width = 6.1}
# png(file = "sim_hc_net_Kernel.png", width = 1.5*9.5, height = 1.5*9.5, units = "cm", res = 300)
fviz_dend(hc_samples, k = 3, cex = 1.5,  k_colors = c("#2E9FDF", "#00AFBB", "#E7B800", "#FC4E07", "#AA4371"),
          color_labels_by_k = TRUE, ggtheme = theme_bw(), horiz = TRUE, main = "Hierarchical clustering of simulated graphs",
          labels_track_height = 0.5) + theme(text = element_text(size = 17), axis.title = element_text(size = 15))
# dev.off()
```

```{r, fig.height = 5, fig.width = 5}
# postscript(file = "sim_hc_tables.eps", width = 8, height = 8, horizontal = FALSE, onefile = FALSE, paper = "special")
dendGraph = fviz_dend(hc_samples, k = 3, cex = 1,  k_colors = c("#2E9FDF", "#00AFBB", "#E7B800", "#FC4E07", "#AA4371")[1:3],
          color_labels_by_k = TRUE, ggtheme = theme_bw(), horiz = TRUE, main = "Hierarchical clustering of simulated networks",
          labels_track_height = 0.5) + theme(text = element_text(size = 12), axis.title = element_text(size = 12)) + 
  theme(plot.margin = unit(c(0,0.1,0,0.1), "cm"), aspect.ratio = 1)
dendGraph
# dev.off()
```

```{r}
ggsave(filename = "Figure7.pdf",  
       plot =  ggarrange(ggdraw(dendGraph, clip = "on", xlim = c(-0.05, 1)),  ggdraw(corrPlot, clip = "on"), ncol = 2, labels = c("A)", "B)")),
       width = 2*15, height = 2*6.5, units = c("cm"))
```

## Consensus network(s)

```{r}
consensus_by_groups = lapply(unique(groups), FUN = function(x){
  list_adj = list_adjacency[names(list_adjacency)%in%names(groups)[groups == x]]
  Adj = Reduce("+", list_adj)
  Adj[Adj<=(0.5*length(list_adj))] = 0
  Adj[Adj>=(0.5*length(list_adj))] = 1
  Adj
})
```

```{r}
round(sapply(consensus_by_groups, FUN = function(A_e){
  sapply(consensus_by_groups_MFA, FUN = function(A_t) sum(abs(as.matrix(A_e) - as.matrix(A_t)))/ncol(A_e)^2)
  }),2)
```

```{r, fig.height = 5, fig.width = 15}
par(mfrow = c(1,3))
qgraph(consensus_by_groups[[1]], 
       shape = "rectangle", vsize = 2, vsize2 = 2.2,
       title = paste0("Consensus on ", paste(names(groups)[groups == 1], collapse = ", ")),
       mar = c(2,2,2,2), color = c("antiquewhite", "aliceblue", "darkorchid3", "forestgreen", "blue")[classif1], diag = FALSE, 
       labels = colnames(consensus_by_groups[[1]]), title.cex = 2,
       label.cex = 1.2, negDashed = TRUE, edge.color = "black", edge.width = 0.5, layout = "spring",
       layout.par = list(repulse.rad = nrow(consensus_by_groups[[1]])^(2.5)))

qgraph(consensus_by_groups[[2]], 
       shape = "rectangle", vsize = 2, vsize2 = 2.2,
       title = paste0("Consensus on ", paste(names(groups)[groups == 2], collapse = ", ")),
       mar = c(2,2,2,2), color =  c("antiquewhite", "aliceblue", "darkorchid3", "forestgreen", "blue")[classif2], diag = FALSE, 
       labels = colnames(consensus_by_groups[[2]]), title.cex = 2,
       label.cex = 1.2, negDashed = TRUE, edge.color = "black", edge.width = 0.5, layout = "spring",
       layout.par = list(repulse.rad = nrow(consensus_by_groups[[2]])^(2.5)))

qgraph(consensus_by_groups[[3]], 
       shape = "rectangle", vsize = 2, vsize2 = 2.2,
       title = paste0("Consensus on ", paste(names(groups)[groups == 3], collapse = ", ")),
       mar = c(2,2,2,2), color =  c("antiquewhite", "aliceblue", "darkorchid3", "forestgreen", "blue")[classif3], diag = FALSE, 
       labels = colnames(consensus_by_groups[[3]]), title.cex = 2,
       label.cex = 1.2, negDashed = TRUE, edge.color = "black", edge.width = 0.5, layout = "spring",
       layout.par = list(repulse.rad = nrow(consensus_by_groups[[3]])^(2.5)))

conGraph = recordPlot()
```

# InfoSession

```{r}
sessionInfo()
```

